\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}

\usepackage{geometry}
\geometry{
  a4paper,
  total={170mm,257mm},
  left=20mm,
  top=20mm,
}

\usepackage{graphicx}
\usepackage{url}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{multicol} 

\definecolor{linkcolor}{HTML}{0073AE}
\definecolor{rulecolor}{HTML}{B6B6B6}

\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    filecolor=magenta,      
    urlcolor=linkcolor,
    citecolor=linkcolor,
    pdftitle={CV},
    pdfauthor={Anu Bazarragchaa},
}

\setlength{\parskip}{0.5em}
\setlist[itemize]{leftmargin=*}

\begin{document}

\begin{center}
    \huge\textbf{Anu Bazarragchaa}
\end{center}

\section*{Personal Information}

\begin{tabular}{l l}
    \textbf{Address:} & 1055 Szent István krt 23., Budapest, HU \\
    \textbf{Phone:} & +36 20 222 5711 \\
    \textbf{Email:} & anubazarragchaa(kukacs)gmail(pont)hu \\
    \textbf{Website:} & \url{https://github.com/anu-bazar} \\
    \textbf{LinkedIn:} & \url{https://www.linkedin.com/in/anu-bazarragchaa/} \\
\end{tabular}

\section*{Education}

\begin{itemize}

    \item \textbf{Bioinformatics MSc} \hfill \textit{2022 - 2024} \\
    Eötvös Lorand University \\
    Budapest, Hungary \\
    \begin{itemize}
        \item Learned data analysis and management using a variety of tools such as Python, R, and SQL. 

        \item Gained experience in analyzing biological data, building predictive models, and designing experiments through coursework such as Statistical Inference, Machine Learning, and Genomics Data Analysis.
        \item GPA: 4.3, Bioinformatics lab - Dr. Eszter Ari lab at ELTE
    \end{itemize}
    
    \item \textbf{Biology BSc} \hfill \textit{2019 - 2022} \\
    University of Debrecen \\
    Debrecen, Hungary \\
    \begin{itemize}
        \item Emphasized yeast genomics, with coursework focused on genetic analysis, molecular biology techniques, and bioinformatics tools such as BLAST and ClustalW. 
        \item Took courses such as Molecular Biology, Genetics, and Genomics of Yeast, analyzing and interpreting genomic data and conducting research in yeast genetics.
        \item GPA 4.8, Summa Cum Laude. Pfliegler's Yeast Lab at UniDeb
    \end{itemize}

    
\end{itemize}

\section*{Experience}

\begin{itemize}
    \item \textbf{Girl Advisor} \hfill \textit{2017 - 2023} \\
    FRIDA Fund \\ 
    Toronto, Canada (Remote)
    \begin{itemize}
        \item Co-Facilitated SSEAP regional advisory from 2021-2022.
        \item Collaborating with local organizations in Mongolia
        \item Conducting needs assessments and providing recommendations for grant funding, resulting in increased support and resources for girls in the SSEAP region.
    \end{itemize}

    \item \textbf{Global Advisory Comittee Member} \hfill \textit{2021 - 2023} \\
    UNGEI \\
    New York, USA (Remote)
    \begin{itemize}
        \item Provided strategic guidance and support to advance girls' education from a Mongolian standpoint.
        \item Collaborating with a diverse group of international stakeholders to develop policies, advocate for resources, and monitor progress towards achieving gender equality in education.
        \item Helped shape and implement initiatives that improved access to education and empowered girls and young women to reach their full potential.
    \end{itemize}
\end{itemize}


\section*{Skills}

\begin{multicols}{2}
\begin{itemize}
    \item Python 3 - NumPy, SciPy, Pandas
    \item JavaScript
    \item Linux - Ubuntu, Debian
    \item C/C++
    \item R
    \item HTML5
    \item CSS3
    \item Java
\end{itemize}
\end{multicols}

\section*{Awards and Honors}

\begin{itemize}
    \item Award of Excellence - Embassy of Mongolia in Hungary 2021-2022
    \item Global 38 Finalists - Microsoft Imagine Cup
\end{itemize}

\section*{Languages}

\begin{itemize}
    \item English - Native Speaker
    \item Mongolian - Native Speaker
    \item Hungarian - Intermediate
\end{itemize}

\section*{References}

Available upon request.



\begin{center}
  \textbf{Made with \LaTeX}
\end{center}
\end{document}
